Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 3.dev

### 2024-10-22 main.tex
an -> and
Added thanks to DEMO guys.

\section*{Acknowledgements}
%
This study follows and draws from experimental and analysis methods originally
developed in unpublished research by Marco Reijne. The authors acknowledge
Felix Dauer, David Gabriel, Sierd Heida, Oliver Maier, Maarten Pelgrim, Marco
Reijne, and Arend Schwab for contributions to the development of the balance
assist bicycle. We acknowledge Shannon van de Velde and Marco Reijne's
development of the bicycle perturbation system. Allen Downey provided useful
insight in the statistical condsiderations. We thank all of the assistants that
helped run the experiments and the participants for their time an enthusiasm.
Thanks to Christoph Schmidt for motivation to do yet another round of trials.
We thank Peter Stahlecker, Benjamin Gonzalez, and Riender Happee for valuable
feedback in early revisions. Lastly, we thank Frans van der Helm for the
consistent encouragement to execute this experiment and his early vision for
obtaining the funding.

>>>>

\section*{Acknowledgements}
%
This study follows and draws from experimental and analysis methods originally
developed in unpublished research by Marco Reijne. The authors acknowledge
Felix Dauer, David Gabriel, Sierd Heida, Oliver Maier, Maarten Pelgrim, Marco
Reijne, and Arend Schwab for contributions to the development of the balance
assist bicycle. We acknowledge Shannon van de Velde and Marco Reijne's
development of the bicycle perturbation system. Allen Downey provided useful
insight in the statistical condsiderations. We thank all of the assistants that
helped run the experiments and the participants for their time and enthusiasm.
Thanks to Wouter Gregoor, Hans van der Does, and Cor Meijneke for reviving the
bicycles at a critical moment. Thanks to Christoph Schmidt for motivation to
do yet another round of trials. We thank Peter Stahlecker, Benjamin Gonzalez,
and Riender Happee for valuable feedback in early revisions. Lastly, we thank
Frans van der Helm for the consistent encouragement to execute this experiment
and his early vision for obtaining the funding.
